---
title: "cc-rmarkdown-testing-DOCUMENT"
author: "Beverly Tan"
date: "06/11/2018"
output: html_document
---

### Loading packages
```{r}
library(dplyr)
library(pander)
```

### Loading biodiversity data
This data is a publicly available dataset of occurrence records for many animal, plant, and fungi species, for 2000-2016 from the NBN Gateway.

```{r}
edidiv <- read.csv("edidiv.csv")
```

### Creating barplot of species richness according to taxonomic group

First creating a table of species richness in each taxonomic group

```{r}
richness <- 
  edidiv %>%
  group_by(taxonGroup) %>%
  summarise(Species_richness = n_distinct(taxonName))

richness

```

Then creating a barplot 

```{r}
barplot(richness$Species_richness, 
        names.arg = richness$taxonGroup, 
        xlab = "Taxa", ylab = "Number of species", 
        ylim = c(0,600)) 
```

### Creating a table showing most common species in each taxonomic group

Determining what the most common species is in each taxonomic group 

```{r}
max_abund <-
  edidiv %>%
  group_by(taxonGroup) %>%
  summarise(taxonName = names(which.max(table(taxonName))))

pander(max_abund)
```

Joining the two data frames together, using "taxonGroup" as the reference

```{r}
richness_abund <- inner_join(richness, max_abund, by = "taxonGroup")
```

Renaming the headers of the tables, and viewing the data frame

```{r}
richness_abund <- rename(richness_abund, Most_abundant =  taxonName, Taxon = taxonGroup)

pander(richness_abund)
```

